Progress

### 2018-07-11 two_dim_majoranas_report/progress.tex
Change folder git

		We indeed find this to be the case. We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
%------------------%		
	\subsection{Varying chemical potential and magnetic field strength}
		From the Pientka paper, we would expect 
			\begin{figure}[H]
				\includegraphics[width=0.3\textwidth]{muB0.png}
				\includegraphics[width=0.3\textwidth]{muB5.png}
				\includegraphics[width=0.3\textwidth]{muB1.png}
				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength.}
			\end{figure}
%------------------%	
	\subsection{Varying spin-orbit}
		\begin{figure}[H]
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a30.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a33.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a36.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a40.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a43.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a46.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a50.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a53.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a56.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%	
	\subsection{Varying superconducting gap}
		\begin{figure}[H]
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d02.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d045.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d067.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d089.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d11.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d133.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d155.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d178.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%
	\subsection{Varying system dimensions}
		Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
			\begin{table}[H]
				\centering
				\begin{tabular}{|c|c|}
					\hline 
					$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
					\hline 
					250 & 1.05 \\ 
					\hline 
					500 & 0.523 \\ 
					\hline 
					1000 & .262 \\ 
					\hline 
					5000 & .0523 \\ 
					\hline 
				\end{tabular} 
				\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
				\label{table:thouless}
			\end{table}

			\begin{figure}[H]
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
				\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
			\end{figure}

			\begin{figure}[H]
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm150.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm200.png}
				\includegraphics[width=0.5\textwidth]{\img/lmgap/lm250.png}
%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
				\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
			\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\printglossaries
\end{document}

>>>>

		We indeed find this to be the case(figure \ref{fig:lmZPpfaf}). We however find that beyond a certain magnetic field strength the bands cross, and the model becomes unphysical.
	%------------------%
	\subsection{Varying system dimensions}
	Widening the junction lowers the Thouless energy, which makes the topological regime accesible at lower magnetic fields, but at the same moment lowering the energy gap.
	\begin{table}[H]
		\centering
		\begin{tabular}{|c|c|}
			\hline 
			$L_\text{m} (nm)$ & $E_\text{Th} (meV)$ \\ 
			\hline 
			250 & 1.05 \\ 
			\hline 
			500 & 0.523 \\ 
			\hline 
			1000 & .262 \\ 
			\hline 
			5000 & .0523 \\ 
			\hline 
		\end{tabular} 
		\caption{Thouless energy for different system widths calculated using \ref{eq:thouless}, asssuming unit transparency.}
		\label{table:thouless}
	\end{table}

	\begin{figure}[H]
		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB250.png}
		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB500.png}
		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB1000.png}
		\includegraphics[width=0.5\textwidth]{\img/lmZPpfaf/pB2000.png}
		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
		\label{fig:lmZPpfaf}
	\end{figure}

	\begin{figure}[H]
		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm100.png}
		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm150.png}
		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm200.png}
		\includegraphics[width=0.5\textwidth]{\img/lmgap/lm250.png}
		%				\includegraphics[width=0.24\textwidth]{\img/lmgap/lm500.png}
		\caption{Topological regime(blue is topological) vs superconducting phase and magnetic field strength, for different strip widths. The lines indicate integer multiples of the Thouless energy, see table \ref{table:thouless}}
		\label{fig:lmZPcurr}
	\end{figure}
%------------------%		
	\subsection{Varying chemical potential and magnetic field strength}
		From the Pientka paper, we would expect 
			\begin{figure}[H]
				\includegraphics[width=0.3\textwidth]{muB0.png}
				\includegraphics[width=0.3\textwidth]{muB5.png}
				\includegraphics[width=0.3\textwidth]{muB1.png}
				\caption{Topological regime(blue is topological) vs chemical potential and magnetic field strength, assuming zeeman field in the superconductor}
			\end{figure}
%------------------%	
	\subsection{Varying spin-orbit}
		\begin{figure}[H]
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a30.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a33.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a36.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a40.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a43.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a46.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a50.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a53.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a56.png}
			\includegraphics[width=0.192\textwidth]{\img/spinorbitZP/a60.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}
%------------------%	
	\subsection{Varying superconducting gap}
		\begin{figure}[H]
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d02.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d045.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d067.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d089.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d11.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d133.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d155.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d178.png}
			\includegraphics[width=0.24\textwidth]{\img/deltagapZPcurrent/d200.png}
			\caption{Phase zeeman plot with increasing spin orbit}
		\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\printglossaries
\end{document}
